Lab 0006: Latent Dirichlet Allocation Applied to Revisions

### 2008-10-23 lda-paper.tex
more lda paper
2008-10-22 23:25:30 abez

@@

%LDA Skeleton
%1. [ ] Abstract 
\begin{abstract}
%2. [ ] Introduction
\section{Introduction}

>>>>

%

In the presence of fine grained changes and detailed changelogs

Developers topics the focus of develop

many changelogs how to sort by change type

interleaved changes relate similar changes

What happened in the previous iteration? What were the developers
working on? What was the developer in the next cubicle working on?
What were the common topics and issues dealt with in the current
release of the software? What were the topics of the previous release?

We propose to extend common concept analysis techniques by executing
them over windows of documents over time. We hope by looking at topic
clusters over time we can I identify continuous effort on a select
group of topics.

Topic analysis of fine-grained revisions is important as often
revisions belonging to different topics are interleaved or even mixed
inside of commits.

@@

%LDA Skeleton
%1. [ ] Abstract 
\begin{abstract}
\end{abstract}
%2. [ ] Introduction
\section{Introduction}
